---
title: "House Insurance Customer Retention"
author: "TEAM-"
date: "05/02/2022"
output:
  html_document:
    toc: TRUE
    number_sections: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# House Insurance Customer Retention
## Preprocessing
### Reading dataset

```{r}
library(readxl)
data <- read.csv("C:/Users/SAIKUMAR/Downloads/Customer_Retention_dataset_R.csv")
head(data,6)
```
### Remove rows with missing Values

```{r}
summary(data)
data <- na.omit(data)
summary(data)

```
### Exploring outliers

```{r}


# On analyzing all the predictor age quantiles there are only outliers in age column. We restrict age values less than 110 years in our analysis.
library(dplyr)
quantile(data$ni.age)

data_age_outlier <- data %>% filter(data$ni.age < 110)
par(mfrow =c(1,2))

boxplot(data$ni.age, xlab="Age",main="Before Outliers")
boxplot(data_age_outlier$ni.age,xlab="Age",main="After Outliers")


#re-assigning data_age_outlier to data
data =  data_age_outlier

```
### Feature Engineering

```{r}



# Drop ID column in data
data = subset(data, select = -c(id) )



# Family column creation (We combined no of adults and children predictors in the dataset to form family size of the household)
family_size <- data$n.adults+data$n.children
data['family_size']=family_size


#Zoning pincode into Zones (We used tableau to localize the zipcodes to locations (states))
zones = c()
zone_idx = as.numeric(substr(data$zip.code, 1, 2))
data['zone_idx']=zone_idx

for (i in data$zone_idx)
{
  if(i==85)
  zones = append(zones, 2)
  else if (i==80)
  zones = append(zones,3)
  else if(i==98)
    zones = append(zones,1)
  else if(i==50)
    zones = append(zones,6)
  else if(i==15)
    zones = append(zones,5)
  else
    zones = append(zones,4)
}

data['zones']=zones

# Removing redundant columns
data = subset(data, select = -c(n.adults,n.children,zone_idx,zip.code) )








```

### Dummy variable creation

```{r}
library(fastDummies)

# Creating dummy variables
data.dummy = data


# Binary data variables ni.gender
data.dummy$ni.gender = ifelse(data.dummy$ni.gender=="M", 1, 0)

# Other data variables house.color, coverage.type, dwelling.type, sales.channel, data.zones 
data.dummy <- dummy_cols(data.dummy, 
                   select_columns = "house.color")


data.dummy <- dummy_cols(data.dummy, 
                   select_columns = "coverage.type")

data.dummy <- dummy_cols(data.dummy,
                   select_columns = "dwelling.type")

data.dummy <- dummy_cols(data.dummy,
                   select_columns = "sales.channel")

data.dummy <- dummy_cols(data.dummy,
                   select_columns = "credit")

data.dummy <- dummy_cols(data.dummy, 
                   select_columns = "zones")

data.dummy <- dummy_cols(data.dummy, select_columns = "year")
data.dummy = subset(data.dummy, select = -c(year,zones,sales.channel,dwelling.type,coverage.type,house.color,credit,year_2016,zones_6,credit_medium,sales.channel_Phone,dwelling.type_Tenant,coverage.type_C,house.color_yellow) )


```

## Data Exploration
### correlation matrix
```{r}

corr.variables <- subset(data.dummy, select = c("ni.age","len.at.res","premium","tenure","family_size"))
cor(corr.variables, use = "complete.obs")

```

### Year Vs Insurance Policy
```{r}
temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2),mgp=c(100,1,0))
counts <- table(temp0$year)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="Year", col=c("blue"))

counts <- table(temp1$year)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="Year", col=c("red"))

sprintf("For kangaroo company, Annually it can observed that the maximum  policy cancellations are in year 2014, whereas it is  following a declining trend till the year 2016, whereas the continuing policies are continuing to increase across the years. ")

```



### Zone Vs Insurance Policy
```{r}

#1 : washington
#2 :  Arizona
#3 :  colorodo
#4 : virginia
#5 : pennyslvania
#6 : others (50 series)

temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))
counts <- table(temp0$zone)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="Zones", col=c("blue"))

counts <- table(temp1$zone)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="Zones", col=c("red"))

sprintf("For kangaroo company, the maximum number of cancelled policy holders are coming from 2,6 i.e Arizona and other parts of USA, whereas least cancellations are coming from virginia and pennyslvania.
The maximum continuing policy holders are coming from Arizona and other parts of USA, whereas least continuing are coming from virginia.
")

```
### house.color Vs Insurance Policy
```{r}



temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2),mgp=c(100,1,0))
counts <- table(temp0$house.color)
barplot(counts, main="continuing customers (cancel=0)",
   xlab="Color", col=c("blue"))

counts <- table(temp1$house.color)
barplot(counts, main="cancelled customers (cancel=1)",
   xlab="Color", col=c("red"))

sprintf("When we observe continuing and cancelled customers, the preferred color of the house is white, followed by blue and red, however there is no differentiation between their choices.")


```

### ni.age Vs Insurance Policy
```{r}



temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2),mgp=c(100,1,0))
boxplot(temp0$ni.age, xlab="Age",main="Continuing customers (credit = 0)", col=c("blue"))
boxplot(temp1$ni.age,xlab="Age",main="Cancelled customers (credit=1)", col=c("red"))

sprintf("For kangaroo company, Age of the customer doesn’t seem to differentiate the customer relationship with the company, however based on quantile range, for cancelled customers, the spread of age is more when compared to continuing customers. ")


```
### len.at.resident Vs Insurance Policy
```{r}



temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))
boxplot(temp0$len.at.res, xlab="len.at.res",main="Continuing customers (credit = 0)", col=c("blue"))
boxplot(temp1$len.at.res,xlab="len.at.res",main="Cancelled customers (credit=1)", col=c("red"))

sprintf("There is not much of a differentiation in distribution in both the cases. But, most of them tend to stay for less period of time.")


```
### credit Vs Insurance Policy
```{r}



temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

counts <- table(temp0$credit)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="Credit", col=c("blue"))

counts <- table(temp1$credit)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="Credit", col=c("red"))

sprintf("It can be seen that, the number of people with high credit score are more in continuing policy holders followed by medium and low. But, for cancelled customers, the trend is high, low and medium. ")



```


### Coverage Vs Insurance Policy
```{r}

#Coverage A:
#Damage to House	
#Covers damage to the house. The face amount of the policy (for example $100,000) is the most you will receive if your house is totally destroyed.

#Coverage B:
#Other Structures	
#Covers damage to other structures or buildings, such as a detached garage, work shed, or fencing.

#Coverage C:
#Personal Property	Covers damage to, or loss of personal property. Personal property includes household contents and other personal belongings used, owned or worn by you and your family.

temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

counts <- table(temp0$coverage.type)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="Coverage", col=c("blue"))

counts <- table(temp1$coverage.type)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="Coverage", col=c("red"))

sprintf("It can be seen that, the order of preference for both continuing and cancelled customers is C,A and B. ")



```
### Dwelling type Vs Insurance Policy
```{r}


temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

counts <- table(temp0$dwelling.type)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="Dwelling", col=c("blue"))

counts <- table(temp1$dwelling.type)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="Dwelling", col=c("red"))

sprintf("It can be seen that the distribution of Dwelling is same for both continuing and cancelled customers.
But, House owning policy holders are majority in continuing and cancelled holders.
  ")



```
### Premium Vs Insurance Policy
```{r}


temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))


boxplot(temp0$premium, xlab="premium",main="Continuing customers (cancel = 0)", col=c("blue"))
boxplot(temp1$premium,xlab="premium",main="Cancelled customers (cancel=1)", col=c("red"))

sprintf("There is not much of a differentiation between continuing and cancelled customers in terms of premium.")



```
### Sales.channel Vs Insurance Policy
```{r}


temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

counts <- table(temp0$sales.channel)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="Sales channel", col=c("blue"))

counts <- table(temp1$sales.channel)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="Sales channel", col=c("red"))

sprintf("For continuing customers, for most of them, the preferred sales channel is broker, whereas, for cancelled customers, the most used mode is phone, followed by broker. ")



```
### ni.gender Vs Insurance Policy
```{r}


temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

counts <- table(temp0$ni.gender)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="Gender", col=c("blue"))

counts <- table(temp1$ni.gender)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="Gender", col=c("red"))

sprintf("In both cases, number of males are greater than number of females.")


```
### ni.marital status Vs Insurance Policy
```{r}


temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

counts <- table(temp0$ni.marital.status)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="Gender", col=c("blue"))

counts <- table(temp1$ni.marital.status)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="Gender", col=c("red"))

sprintf("Most of them are married in both the cases. ")



```
### tenure Vs Insurance Policy
```{r}


temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

boxplot(temp0$premium, xlab="tenure",main="Continuing customers (cancel = 0)", col=c("blue"))
boxplot(temp1$premium,xlab="tenure",main="Cancelled customers (cancel=1)", col=c("red"))

sprintf("Not much differentiation with respect to tenure between continuing and cancelled policies  ")

```
### claim.ind Vs Insurance Policy
```{r}


temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

counts <- table(temp0$claim.ind)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="claim.id", col=c("blue"))

counts <- table(temp1$claim.ind)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="claim.id", col=c("red"))

sprintf("For policies that are cancelled, holders tend to show high claim rate compared to continuing policies ")

```
### n.family_size Vs Insurance Policy
```{r}


temp1 = data[data$cancel==1,]
temp0 = data[data$cancel==0,]
par(mfrow =c(1,2))

counts <- table(temp0$family_size)
barplot(counts, main="continuing policy holders (cancel=0)",
   xlab="family_size", col=c("blue"))

counts <- table(temp1$family_size)
barplot(counts, main="cancelled policy holders (cancel=1)",
   xlab="family_size", col=c("red"))

sprintf("There are not much differentiations between continuing and cancelled polcies w.r.t family size, however the higher the family size, the higher the probability the customer is tending to cancel the policy.")

```


## Distribution
### Age distribution

```{r}
# Following are continuous predictors: ni.age, len.at.res, premium, family_size, tenure
par(mfrow=c(2,1))
hist(data$ni.age,breaks = 100)
hist(log(data$ni.age),breaks = 100)
```

### len.at.res distribution

```{r}
# Following are continuous predictors: ni.age, len.at.res, premium, family_size, tenure
par(mfrow=c(3,1))
hist(data$len.at.res,breaks = 100)
hist(log(data$len.at.res),breaks = 100)
hist(log(data$len.at.res)^2,breaks = 100)
```



###  Premium distribution
```{r}
# Following are continuous predictors: ni.age, len.at.res, premium, family_size, tenure
par(mfrow=c(2,1))
hist(data$premium,breaks = 100)
hist((data$premium-mean(data$premium))/(sd(data$premium)),breaks = 100)
```

###  Family size distribution
```{r}
# Following are continuous predictors: ni.age, len.at.res, premium, family_size, tenure
# Following are continuous predictors: ni.age, len.at.res, premium, family_size, tenure
par(mfrow=c(2,1))
hist(data$family_size,breaks = 100)
hist(log(data$family_size),breaks = 100)
```


###  Tenure distribution
```{r}
# The peaks clearly indicte that there are two groups in the dataset that is maintaining tenure between 0-10 and another group 10-20
par(mfrow=c(2,1))
hist(data$tenure,breaks = 100)
hist((data$tenure-mean(data$tenure))/(sd(data$tenure)),breaks = 100)
```



## Data Normalization and splits
### Data Normalization

```{r}

# Following are continuous predictors: ni.age, len.at.res, premium, family_size, tenure


# Data is dataframe without dummy variable creation

data$ni.age =  log(data$ni.age)
data$premium =  (data$premium-mean(data$premium))/sd(data$premium)
data$len.at.res =  log(data$len.at.res)^2
data$Family_size =  log(data$family_size)
data$tenure =  (data$tenure-mean(data$tenure))/sd(data$tenure)

# Data.dummy is dataframe with dummy variables (n-1)

data.dummy$ni.age =  log(data.dummy$ni.age)
data.dummy$premium =  (data.dummy$premium-mean(data.dummy$premium))/sd(data.dummy$premium)
data.dummy$len.at.res =  log(data.dummy$len.at.res)^2
data.dummy$family_size =  log(data.dummy$family_size)
data.dummy$tenure =  (data.dummy$tenure-mean(data.dummy$tenure))/sd(data.dummy$tenure)


```

### Data split

```{r}


##################### data
set.seed(123)
split <- sample(c(rep(0, 0.7 * nrow(data)), rep(1, 0.3 * nrow(data))))

train <- data[split == 0, ] 


# train_x,train_y,test_x,test_y
#splitting further
train_x <- subset(data, select = -c(cancel) )
train_y <- data$cancel

test <- data[split == 1, ] 

#splitting further
test_x <- subset(test, select = -c(cancel) )
test_y <- test$cancel

###################### Dummy data

#Dummy dataset

splitd <- sample(c(rep(0, 0.7 * nrow(data.dummy)), rep(1, 0.3 * nrow(data.dummy))))

traind <- data.dummy[splitd == 0, ] 


# traind_x,traind_y,testd_x,testd_y
#splitting further
traind_x <- subset(data.dummy, select = -c(cancel) )
traind_y <- data.dummy$cancel

testd <- data.dummy[split == 1, ] 

#splitting further
testd_x <- subset(testd, select = -c(cancel) )
testd_y <- testd$cancel



```

## Quantitative Metrics
###  Confusion Matrix
```{r}
Accuracy <- function(preds,actual)
{

confusionMatrix(as.factor(preds), as.factor(actual),positive="1")

}

```


### ROC Curve
```{r}

plot_ROC <- function(preds,actual)
{
library("ROCR")
pred.2 <- prediction(preds,actual)
perf <- performance(pred.2, "tpr", "fpr")
auc.perf <- performance(pred.2,"auc") 
auc.perf@y.values
plot(perf, main = paste("Area under the curve", round(as.numeric(auc.perf@y.values),4)))
abline(0,1)
}

```


### Lift Curve

```{r}
plot_lift=function(preds,actual)
{
pred.2 <- prediction(preds,actual)
perf1=performance(pred.2,"lift","rpp")
plot(perf1, main="Lift curve",colorsize=T)
}

```



### F1 Curve
```{r}

plot_F <- function(probs,actual)
{
F_values <- c() 
for (cut_off in seq(0,1,0.01) )
{
#preds <- predict(logistic.mod, type = "response")
preds.1 <- ifelse(probs > cut_off, 1, 0)
tp <- sum((actual == 1) & (preds.1 == 1))
tn <- sum((actual ==0) & (preds.1 == 0))
fp <- sum((actual == 0) & (preds.1 == 1))
fn <- sum((actual == 1) & (preds.1 == 0))
F1 <- tp/(tp+(fp+fn)/2)
F_values = append(F_values, F1)

}
  

cut_off = seq(0,1,0.01)
# creating dataframe
df = data.frame(F_values,cut_off)
dfMax <- df[ which(max(df$F_values) == df$F_values), ]



plot(cut_off,F_values,main = "Plot: F Score Vs Threshold ",col="blue")
lines(F_values~cut_off)


#abline(v = dfMax['cut_off'], col="red", lwd=3, lty=2)


#sprintf("The cut off value where F score is maximum is %f", dfMax['cut_off'])
  
}

```


## Handling Imbalanced classes
```{r}
prop.table(table(data$cancel))
library("ROSE")

```
### Under Sampling
```{r}
under <- ovun.sample(cancel~., data=train, method = "under", N = 10000 )$data
underd <- ovun.sample(cancel~., data=traind, method = "under", N = 10000 )$data

table(under$cancel)

# Training split for under sampling
under_x <- subset(under, select = -c(cancel) )
under_y <- under$cancel


# Training split for dummy under sampling
underd_x <- subset(underd, select = -c(cancel) )
underd_y <- underd$cancel

```

### Over Sampling
```{r}
over <- ovun.sample(cancel~., data = train, method = "over", N = 30000)$data
overd <- ovun.sample(cancel~., data = traind, method = "over", N = 30000)$data
table(over$cancel)



# Training split for under sampling
over_x <- subset(over, select = -c(cancel) )
over_y <- over$cancel


# Training split for dummy under sampling
overd_x <- subset(overd, select = -c(cancel) )
overd_y <- overd$cancel




```



## Modeling Techniques

```{r}
# train_x, train_y, test_x, test_y
# Dummy: traind_x, traind_y, testd_x, testd_y

#under_x, under_y
#Under Sampling: Dummy: underd_x, underd_y

#over_x, over_y
#Over Sampling: Dummy: overd_x, overd_y


```


###  Logistic Regression (With All features)
#### Modeling
```{r}

logistic.model <- glm(cancel ~ year+house.color+ni.age+len.at.res+credit+coverage.type+dwelling.type+premium+sales.channel+ni.gender+ni.marital.status+tenure+claim.ind+family_size+zones , family=binomial("logit"),
                    data=train)


under_logistic.model <- glm(cancel ~ year+house.color+ni.age+len.at.res+credit+coverage.type+dwelling.type+premium+sales.channel+ni.gender+ni.marital.status+tenure+claim.ind+family_size+zones , family=binomial("logit"),
                    data=under)

over_logistic.model <- glm(cancel ~ year+house.color+ni.age+len.at.res+credit+coverage.type+dwelling.type+premium+sales.channel+ni.gender+ni.marital.status+tenure+claim.ind+family_size+zones , family=binomial("logit"),
                    data=over)

summary(over_logistic.model)


```
#### Test
```{r}
library("caret")


# Without any sampling
prob_train <- logistic.model %>% predict(train_x, type = "response")
prob <- logistic.model %>% predict(test_x, type = "response")

preds_train <- ifelse(prob_train > 0.5,1 , 0)
preds <- ifelse(prob > 0.5,1 , 0)




# With under sampling
train_under_prob <- under_logistic.model %>% predict(under_x, type = "response")
under_prob <- under_logistic.model %>% predict(test_x, type = "response")

train_under_preds <- ifelse(train_under_prob > 0.5,1 , 0)
under_preds <- ifelse(under_prob > 0.5,1 , 0)



#With Over sampling
train_over_prob <- over_logistic.model %>% predict(over_x, type = "response")
over_prob <- over_logistic.model %>% predict(test_x, type = "response")

train_over_preds <- ifelse(train_over_prob > 0.5,1 , 0)
over_preds <- ifelse(over_prob > 0.5,1 , 0)



## As we observed the number of tp has increased with under and over sampling, under sampling gave better tp count. Over sampling gave better accuracy.

```
#### Train Metrics
```{r}

### Please find train and test accuracies.

# Without sampling
Accuracy(preds_train,train_y)

#Under Sampling
Accuracy(train_under_preds,under_y)

#Over Sampling
Accuracy(train_over_preds,over_y)
```

#### Test Metrics
```{r}

### Please find train and test accuracies.

# Without sampling

Accuracy(preds,test_y)
plot_ROC(preds,test_y)
plot_lift(preds,test_y)
plot_F(prob,test_y)


#Under Sampling

Accuracy(under_preds,test_y)
plot_ROC(under_preds,test_y)
plot_lift(under_preds,test_y)
plot_F(under_prob,test_y)

#Over Sampling

Accuracy(over_preds,test_y)
plot_ROC(over_preds,test_y)
plot_lift(over_preds,test_y)
plot_F(over_prob,test_y)




```

###  Logistic Regression (With significant features)
```{r}

summary(over_logistic.model)

# We picked over sampled model for further analysis. On reviewing the summary of logistic model, we identified year, ni.age, len.at.res, credit, premium. ni.marital.status, tenure, claim.ind. family_size, zones are statistically significant. Now we perform logistic regression using above features.

```

#### Modeling
```{r}

SS.logistic.model <- glm(cancel ~ year+ni.age+len.at.res+credit+premium+ni.marital.status+tenure+claim.ind+family_size+zones , family=binomial("logit"),
                    data=train)


SS.under_logistic.model <- glm(cancel ~ year+ni.age+len.at.res+credit+premium+ni.marital.status+tenure+claim.ind+family_size+zones , family=binomial("logit"),
                    data=under)

SS.over_logistic.model <- glm(cancel ~ year+ni.age+len.at.res+credit+premium+ni.marital.status+tenure+claim.ind+family_size+zones , family=binomial("logit"),
                    data=over)


summary(SS.over_logistic.model)

```
#### Test
```{r}
library("caret")


# Without any sampling
prob <- SS.logistic.model %>% predict(test_x, type = "response")
prob_train <- SS.logistic.model %>% predict(train_x, type = "response")
preds <- ifelse(prob > 0.5,1 , 0)
preds_train <- ifelse(prob_train > 0.5,1 , 0)




# With under sampling
under_prob <- SS.under_logistic.model %>% predict(test_x, type = "response")
under_prob_train <- SS.under_logistic.model %>% predict(under_x, type = "response")

under_preds <- ifelse(under_prob > 0.5,1 , 0)
under_preds_train <- ifelse(under_prob_train > 0.5,1 , 0)



#With Over sampling

over_prob <- SS.over_logistic.model %>% predict(test_x, type = "response")
over_prob_train <- SS.over_logistic.model %>% predict(over_x, type = "response")
over_preds <- ifelse(over_prob > 0.5,1 , 0)
over_preds_train <- ifelse(over_prob_train > 0.5,1 , 0)






## As we observed the accuracy has dropped significantly by taking only statistically significant features.

```
#### Train Metrics
```{r}

### Please find train and test accuracies.

# Without sampling
Accuracy(preds_train,train_y)

#Under Sampling
Accuracy(under_preds_train,under_y)

#Over Sampling
Accuracy(over_preds_train,over_y)
```

#### Test Metrics 
```{r}
library("caret")


# Without any sampling
prob <- SS.logistic.model %>% predict(test_x, type = "response")

preds <- ifelse(prob > 0.5,1 , 0)

Accuracy(preds,test_y)
plot_ROC(preds,test_y)
plot_lift(preds,test_y)
plot_F(prob,test_y)



# With under sampling
under_prob <- SS.under_logistic.model %>% predict(test_x, type = "response")

under_preds <- ifelse(under_prob > 0.5,1 , 0)

Accuracy(under_preds,test_y)
plot_ROC(under_preds,test_y)
plot_lift(under_preds,test_y)
plot_F(under_prob,test_y)


#With Over sampling

over_prob <- SS.over_logistic.model %>% predict(test_x, type = "response")

over_preds <- ifelse(over_prob > 0.5,1 , 0)

Accuracy(over_preds,test_y)


plot_ROC(over_preds,test_y)
plot_lift(over_preds,test_y)
plot_F(over_prob,test_y)



## As we observed the accuracy has dropped significantly by taking only statistically significant features.
```



###  Decision Tree
```{r}
library(rpart)
library(rpart.plot)

```
#### Modeling
```{r}





DT_fit1 <- rpart(cancel ~., data = overd, method = 'class')


rpart.plot(DT_fit1, extra = 106)


```
#### Test
```{r}


DT_preds <-predict(DT_fit1, testd_x, type = 'prob')
DT_class <- ifelse(DT_preds[,1] > DT_preds[,2],0 , 1)
DT_probs <- ifelse(DT_preds[,1] > DT_preds[,2],DT_preds[,1] , DT_preds[,2])



```

#### Train Metrics
```{r}


DT_preds1 <-predict(DT_fit1, overd_x, type = 'prob')
DT_class1 <- ifelse(DT_preds1[,1] > DT_preds1[,2],0 , 1)
DT_probs1 <- ifelse(DT_preds1[,1] > DT_preds1[,2],DT_preds1[,1] , DT_preds1[,2])

Accuracy(DT_class1,overd_y)


```

#### Test Metrics
```{r}


Accuracy(DT_class,testd_y)
plot_ROC(DT_class,testd_y)
plot_lift(DT_class,testd_y)
plot_F(DT_probs,testd_y)
```


###  Random Forest classifer
```{r}
#install.packages("randomForest")
library("randomForest")

```
#### Modeling
```{r}
overd$cancel <- as.character(overd$cancel)
overd$cancel <- as.factor(overd$cancel)

rf <- randomForest(cancel~., data=overd)
print(rf)



```
#### Test
```{r}


RF_preds <-predict(rf, testd_x, type = 'prob')
RF_class <- ifelse(RF_preds[,1] > RF_preds[,2],0 , 1)
RF_probs <- ifelse(RF_preds[,1] > RF_preds[,2],RF_preds[,1] , RF_preds[,2])



```
#### Train Metrics
```{r}



RF_preds1 <-predict(rf, overd_x, type = 'prob')
RF_class1 <- ifelse(RF_preds1[,1] > RF_preds1[,2],0 , 1)
RF_probs1 <- ifelse(RF_preds1[,1] > RF_preds1[,2],RF_preds1[,1] , RF_preds1[,2])

Accuracy(RF_class1,overd_y)


```
#### Test Metrics
```{r}

Accuracy(RF_class,testd_y)
plot_ROC(RF_class,testd_y)
plot_lift(RF_class,testd_y)
plot_F(RF_probs,testd_y)
 



```



###  XGboost
```{r}
library("xgboost")

```
#### Modeling
```{r}
library("xgboost")
xgb_train <- xgb.DMatrix(data = as.matrix(overd_x), label = overd_y)

xgb_params <- list( 
 eta = 0.1,
 max_depth = 10, 
 gamma=1,
 subsample = 0.5,
 colsample_bytree = 0.5,
 eval_metric = "merror",
 objective = "multi:softprob",
 num_class = length(unique(data.dummy$cancel))
)



xgb_model <- xgb.train(
  params = xgb_params,
  data = xgb_train,
  nrounds = 1000,
  verbose = 1
)
xgb_model


```
#### Test
```{r}

#xgb_test <- xgb.DMatrix(data = as.matrix(testd_x), label = testd_y)
XGB_preds <- predict(xgb_model, as.matrix(testd_x), reshape = TRUE)
XGB_class <- ifelse(XGB_preds[,1] > XGB_preds[,2],0 , 1)
XGB_probs <- ifelse(XGB_preds[,1] > XGB_preds[,2],XGB_preds[,1] , XGB_preds[,2])
xgb.plot.importance(importance_matrix = xgb.importance(colnames(xgb_train), xgb_model))


```

#### Train Metrics
```{r}

#xgb_test <- xgb.DMatrix(data = as.matrix(testd_x), label = testd_y)
XGB_preds1 <- predict(xgb_model, as.matrix(overd_x), reshape = TRUE)
XGB_class1 <- ifelse(XGB_preds1[,1] > XGB_preds1[,2],0 , 1)
XGB_probs1 <- ifelse(XGB_preds1[,1] > XGB_preds1[,2],XGB_preds1[,1] , XGB_preds1[,2])


Accuracy(XGB_class1,overd_y)
plot_ROC(XGB_class1,overd_y)

```


#### Test Metrics
```{r}



Accuracy(XGB_class,testd_y)
plot_ROC(XGB_class,testd_y)
plot_lift(XGB_class,testd_y)
plot_F(XGB_probs,testd_y)

```

###  Majority voting
```{r}
#Voting among XGB_class,RF_class,DT_class

```
#### Average
```{r}
library(modeest)
ensemble_class = cbind(XGB_class,RF_class,DT_class)


ensemble_preds = apply(ensemble_class,1,function(x) names(which.max(table(x))))

ensemble_preds = as.integer(ensemble_preds)
Accuracy(ensemble_preds,testd_y)
plot_ROC(ensemble_preds,testd_y)
plot_lift(ensemble_preds,testd_y)


```


